Machine Learning guided workflow for Ribosome Binding Site engineering

### 2021-05-12 paper/main.tex
fix bugs for local env

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[maxcitenames=1,style=numeric]{biblatex}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{tcolorbox}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{thmtools}
\usepackage{thm-restate}
\usepackage{enumerate}
\usepackage{xcolor}
\usepackage{textgreek}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{authblk}
% \usepackage{subfigure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.32]{paper/plots/Main_Paper/swarmplot.pdf}
    \includegraphics[scale=0.32]{paper/plots/Main_Paper/quantplot.pdf}
    \caption{\textbf{TIRs of RBS groups examined in this study.} A) Swarm plot showing the obtained TIRs divided into RBS groups. BPS-NC: base-by-base changes in the non-core region. BPS-C: base-by-base changes in the core region. UNI: Randomly generated sequences with uniform distribution. PPM: Randomly generated sequences with distribution following the PPM for all natural RBS in \emph{E. coli}. Bandit0/1/2/3 - Bandit algorithm generated results for Round 0, 1, 2 and 3 respectively. SD - Shine-Dalgarno sequence. B) Plot showing highest TIR obtained in a given quantile of results divided into groups as in A), save the random groups which were shown together due to similar distributions.}
    \label{fig: Swarmplot and Quantplot}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.32]{paper/plots/Main_Paper/scatter_abc1_FF.pdf}
    \caption{Scatterplot.}
    \label{fig: Scatterplot}
\end{figure}

@@

\input{methods}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[maxcitenames=1,style=numeric]{biblatex}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{tcolorbox}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{thmtools}
\usepackage{thm-restate}
\usepackage{enumerate}
\usepackage{xcolor}
\usepackage{textgreek}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{authblk}
% \usepackage{subfloat}

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.32]{plots/Main_Paper/swarmplot.pdf}
    \includegraphics[scale=0.32]{plots/Main_Paper/quantplot.pdf}
    \caption{\textbf{TIRs of RBS groups examined in this study.} A) Swarm plot showing the obtained TIRs divided into RBS groups. BPS-NC: base-by-base changes in the non-core region. BPS-C: base-by-base changes in the core region. UNI: Randomly generated sequences with uniform distribution. PPM: Randomly generated sequences with distribution following the PPM for all natural RBS in \emph{E. coli}. Bandit0/1/2/3 - Bandit algorithm generated results for Round 0, 1, 2 and 3 respectively. SD - Shine-Dalgarno sequence. B) Plot showing highest TIR obtained in a given quantile of results divided into groups as in A), save the random groups which were shown together due to similar distributions.}
    \label{fig: Swarmplot and Quantplot}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.32]{plots/Main_Paper/scatter_abc1_FF.pdf}
    \caption{Scatterplot.}
    \label{fig: Scatterplot}
\end{figure}

@@

\input{methods.tex}

### 2021-05-12 paper/methods.tex
fix bugs for local env

\textbf{Plasmid Design.}
The pBbB6c-GFP plasmid has been used for all our designs.
This plasmid comes with GFP mut3b CDS inducible with addition of Isopropyl β-D-1-thiogalactopyranoside (IPTG).
The original RBS for the GFP CDS was replaced with combination of PCR and isothermal assembly.
Primers and the assembly strategy have been generated using the Teselagen DESIGN software (Teselagen Biotechnology).

@@

\textbf{Sequencing}
Strains that gave GFP fluorescence intensity readings similar to that of the original RBS were selected for sequence confirmation by capillary electrophoresis sequencing (CES) by Macrogen, Inc. (Seoul, South Korea).
The strains transformed with each of the selected constructs were grown to saturation in 5 mL LB medium with chloramphenicol selection (34 µg/mL).
Plasmids were extracted from the cultures using the QIAprep Spin Miniprep Kit (QIAGEN) according to the manufacturer’s instructions.
Plasmid concentrations were quantified using the Cytation 5 plate reader with the Take3 Micro-Volume Plate (BioTek) and all fell in the range of 100-200 ng/µL.
Samples of 20 µL of undiluted plasmid DNA were sequenced using a single primer (5’-CGATATAGGCGCCAGCAA-3’) that binds approximately 150 bp upstream of the RBS.
Reads were aligned with the template sequence in the Teselagen software (TeselaGen Biotechnology, Inc.).

@@

\begin{figure}[t]
\centering
\subfloat{\label{main:c}\includegraphics[scale=.4]{plots/Recommend_2_Data_Point_Top_2_UCB.pdf}}\par\medskip
\begin{minipage}{.5\linewidth}
\centering
\subfloat[]{\label{main:a}\includegraphics[scale=.4]{plots/GP-BUCB_Recommend_1st_Data_Point.pdf}}
\end{minipage}%
\begin{minipage}{.5\linewidth}
\centering
\subfloat[]{\label{main:b}\includegraphics[scale=.4]{plots/GP-BUCB_Recommend_2nd_Data_Point.pdf}}
\end{minipage}
\caption{Batch Recommendation. We use the batch size of 2, with 5 initial observations. The design (recommendation) space is 24 uniformly distributed points in the range [-2,10], i.e. {-2, -1.5, -1, ..., 9.5, 10}.
The confidence interval are shown with predicted mean of $\pm$ 1.96 standard deviation.
(a) Top UCB recommendations. The recommendations are 2 data points with top UCB scores, constructed with GP predictions. 
(b)(c) GP-BUCB recommendations. (b) shows the first recommended sequence, (c) shows the new predicted confidence interval and the second recommendation based on that.}
\label{fig:batch rec}
\end{figure}

>>>>

\textbf{Plasmid Design.}
The pBbB6c-GFP plasmid has been used for all our designs.
This plasmid comes with GFP mut3b CDS inducible with addition of Isopropyl $\beta$-D-1-thiogalactopyranoside (IPTG).
The original RBS for the GFP CDS was replaced with combination of PCR and isothermal assembly.
Primers and the assembly strategy have been generated using the Teselagen DESIGN software (Teselagen Biotechnology).

@@

\textbf{Sequencing}
Strains that gave GFP fluorescence intensity readings similar to that of the original RBS were selected for sequence confirmation by capillary electrophoresis sequencing (CES) by Macrogen, Inc. (Seoul, South Korea).
The strains transformed with each of the selected constructs were grown to saturation in 5 mL LB medium with chloramphenicol selection (34 $\mu$g/mL).
Plasmids were extracted from the cultures using the QIAprep Spin Miniprep Kit (QIAGEN) according to the manufacturer’s instructions.
Plasmid concentrations were quantified using the Cytation 5 plate reader with the Take3 Micro-Volume Plate (BioTek) and all fell in the range of 100-200 ng/$\mu$L.
Samples of 20 $\mu$L of undiluted plasmid DNA were sequenced using a single primer (5’-CGATATAGGCGCCAGCAA-3’) that binds approximately 150 bp upstream of the RBS.
Reads were aligned with the template sequence in the Teselagen software (TeselaGen Biotechnology, Inc.).

@@

% \begin{figure}[t]
% \centering
% \subfloat{\label{main:c}\includegraphics[scale=.4]{plots/Recommend_2_Data_Point_Top_2_UCB.pdf}}\par\medskip
% \begin{minipage}{.5\linewidth}
% \centering
% \subfloat{\label{main:a}\includegraphics[scale=.4]{plots/GP-BUCB_Recommend_1st_Data_Point.pdf}}
% \end{minipage}%
% \begin{minipage}{.5\linewidth}
% \centering
% \subfloat{\label{main:b}\includegraphics[scale=.4]{plots/GP-BUCB_Recommend_2nd_Data_Point.pdf}}
% \end{minipage}
% \caption{Batch Recommendation. We use the batch size of 2, with 5 initial observations. The design (recommendation) space is 24 uniformly distributed points in the range [-2,10], i.e. {-2, -1.5, -1, ..., 9.5, 10}.
% The confidence interval are shown with predicted mean of $\pm$ 1.96 standard deviation.
% (a) Top UCB recommendations. The recommendations are 2 data points with top UCB scores, constructed with GP predictions. 
% (b)(c) GP-BUCB recommendations. (b) shows the first recommended sequence, (c) shows the new predicted confidence interval and the second recommendation based on that.}
% \label{fig:batch rec}
% \end{figure}

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \includegraphics[scale=.4]{plots/Recommend_2_Data_Point_Top_2_UCB.pdf}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \includegraphics[scale=0.4]{plots/GP-BUCB_Recommend_1st_Data_Point.pdf}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \includegraphics[scale=0.4]{plots/GP-BUCB_Recommend_2nd_Data_Point.pdf}
    \end{subfigure}
    \caption{Batch Recommendation. We use the batch size of 2, with 5 initial observations. The design (recommendation) space is 24 uniformly distributed points in the range [-2,10], i.e. {-2, -1.5, -1, ..., 9.5, 10}.
    The confidence interval are shown with predicted mean of $\pm$ 1.96 standard deviation.
    (a) Top UCB recommendations. The recommendations are 2 data points with top UCB scores, constructed with GP predictions. 
    (b)(c) GP-BUCB recommendations. (b) shows the first recommended sequence, (c) shows the new predicted confidence interval and the second recommendation based on that.}
    \label{fig:batch rec}
\end{figure}
